Network Structure, Efficiency, and Performance in WikiProjects

### 2018-04-04 paper-content.tex
Daniel's revisions.

The internet has enabled collaborations at a global scale.
Wikipedia, a free encyclopedia that invites anyone to edit articles,
is one of the most successful and visible examples of such a collaboration.
Organizing groups, even small ones, without top-down control is notoriously
difficult
\cite{freeman_tyranny_1972},
and yet Wikipedia, with millions of self-organized editors,
has produced a high-quality encyclopedia \cite{giles_internet_2005,keegan_evolution_2017}.
A better theoretical understanding of projects like Wikipedia is highly desirable as it could
help inform the design of new collaborative projects.
We focus on one aspect of organizing a large-scale decentralized collaboration:
the network structure \cite{newman_structure_2003}.
How does Wikipedia's non-hierarchical structure relate to its success?

We look specifically at WikiProjects on the English-language Wikipedia.
WikiProjects are collections of thematically related articles,
each with their own standards, norms, and processes.
When measuring the quality of collaborative projects,
there are at least two distinct measures to consider.
The first measure is short-term:
how effective a unit of work is at improving
the collaboration's output,
which we call {\em efficiency}.
The other measure is long-term:
the highest quality typically reached by an output,
which we call {\em performance}.
These two terms are often used interchangeably,
but we find it fruitful to distinguish between the two concepts.
We find that Wikipedia, like many other collaborations,
exhibits an overall trade-off between performance and efficiency.
However, some WikiProjects are higher in both efficiency and performance
than others,
suggesting the existence of factors that correlate positively with both.

@@

Our main findings are:
\begin{itemize}
\item Despite an overall performance/efficiency trade-off,
WikiProjects having low-degree coeditor networks tend to have both higher performance and higher efficiency;
\item Short path lengths tend to be associated with higher performance, consistent with a conformity-based learning strategy;
\item Structural inequality, as measured by degree skewness, is associated with lower performance;
\item Our agent-based model
shows that the efficiency and performance of collaborations can
depend on network degree,
and that the direction of that dependence varies with social learning strategy.
\end{itemize}

@@

\section{Background and Related Work}
\label{sec:background}
The present paper investigates the relationship between social networks
and collaboration outcomes.
This connection has been explored by a number of theoretical,
numerical, and small-scale lab studies in the field of
{\em social learning}.
We expand the literature with a large-scale, empirical field study.
In much of the existing literature,
degree distribution correlates with outcome measures.
But aside from the naive Bayes case, it is unknown whether
the correlation is explained best by degree or by another structural property
correlated with degree, such as characteristic path length.
In the empirical networks we study,
unlike artificial networks,
the structural properties vary independently,
making it easier to isolate individual
network properties that correlate with outcome variables.

@@

{\bf Lab experiments.} Lab-based experiments on networked collaboration
suggest a complex interaction between network topology,
and other factors.
While groups of networked human subjects reliably perform very well on
difficult graph-coloring tasks, the best performing network architectures
(e.g., fully-connected vs. small-world) vary
from task to task \cite{kearns_experiments_2012}.
The same studies found that while human subjects tend to perform very well on
a number of networks, they perform worst on self-organized
networks.
Similarly, some network topologies are able to reach faster decisions in the
presence of more information, while others show the opposite effect
\cite{kearns_experimental_2006}.
Based on lab experiments, Fowler and Christakis \shortcite{fowler_cooperative_2010}
suggest that individual decisions towards altruism are conditional on their
neighbor's behavior and ``contagious'' up to three degrees away.
Later experiments by Suri and Watts \shortcite{suri_cooperation_2011} confirmed the
existence of conditional altruism,
but concluded that altruistic
behavior only influences first-degree neighbors.

@@

For Wikipedia specifically,
Robert and Romero \shortcite{robert_crowd_2015} found that
larger group sizes yield higher article ratings
when the groups are diverse and experienced.
Also on Wikipedia,
Kittur and Kraut found that different types of coordination have a complex
effect on the quality of Wikipedia articles \shortcite{kittur_harnessing_2008}.
Both explicit and implicit coordination result in higher quality articles,
with explicit coordination being especially central in the early life of an
article.
Shaw and Hill \shortcite{shaw_laboratories_2014}
found that behavior in online wiki communities is consistent
with the ``iron law of oligarchy,''
which states that
earlier members of a group will, over time, gain disproportionate
decision-making power and act increasingly out of self-interest rather than
the good of the group \cite{michels_political_1999}.
Similarly, Halfaker et al. \shortcite{halfaker_rise_2013} attributed decreasing
participation on Wikipedia to poor retention of new users.
Looking specifically at Wikipedia policies determined by editor consensus,
Keegan and Fiesler \shortcite{keegan_evolution_2017} found a trend
from flexible rule-making towards less flexible maintenance and deliberation.
Using content analysis,
Morgan et al. \shortcite{morgan_project_2013} found WikiProjects to be
more loosely organized than traditional teams.

@@

Our analysis combines multiple data sets from the English-language Wikipedia.
For information about edit history, we used a publicly-available data set containing
metadata (time, article id, user) about all edits from July 12, 2006 to December 2, 2015.
We used a custom script to scrape article quality assessments from logs produced
by WP 1.0 Bot for 2279 unique WikiProjects
between May 4, 2006 and December 2, 2015.
Finally, we used a publicly-available database dump of page events (including rename events)
to reconstruct the article id for each title mentioned in the assessment logs.

@@

The {\em coeditor network} of a WikiProject consists of nodes representing editors,
and edges connecting any editors who have edited the same article.
The edges are directed, with the direction representing the direction of
{\em plausible information flow};
an edge from Alice to Bob exists if Alice edited an article and then Bob edited the same article at
a later time.
Edges can exist in both directions e.g.,
if an article was edited first by Alice, then by Bob, and again by Alice.
We make the simplifying assumption of unit weight for all edges.
We focus on three structural properties:
degree, characteristic path length, and min-cut.
Degree and characteristic path length have been shown to correlate with
performance and efficiency in some social learning settings
\cite{golub_naive_2010,mason_propagation_2008,grim_scientific_2013},
while min-cut can be interpreted as a measure of decentralization,
common feature of peer-produced communities such as Wikipedia
\cite{benkler_wealth_2006}.

The degree distribution is the simplest network property we analyze.
The in-degree (out-degree) of a node is the number of edges to (from) that node.
Taking the average of either in-degree or out-degree gives the same value:
the {\em mean degree} of the network.
In our context, the mean degree represents how many others a given editor has collaborated with.
We also consider the {\em skewness} of the in-degree and out-degree distributions.
A large positive degree skewness value for a WikiProject coeditor network
implies that a small number of editors have a very large number of collaborators,
while a small positive value implies that the editors having the most collaborators
don't have many more than a typical editor.

We also calculate the characteristic path length for each WikiProject coeditor network.
The {\em distance} from node $s$ to node $t$ is the distance of the shortest path
from $s$ to $t$.
The {\em characteristic path length} (or just {\em path length} for brevity)
is the mean distance between all editor pairs,
excluding unconnected pairs.
To account for unconnected nodes, we also measure the {\em connected fraction}:
the fraction of ordered node pairs with a directed path from source to sink.
The path length represents how quickly information can move through the network.
Networks with longer paths require more interactions for information to propagate through
the network,
which has been shown to reduce efficiency in some settings
\cite{mason_propagation_2008,barkoczi_social_2016}.

Our final network measure quantifies the connectivity of a project's coeditor network using
min-cut size.
The minimum $st$-cut between nodes $s$ and $t$ is the set of edges that must be removed in order that
no path exists from $s$ to $t$.
The minimum cut (min-cut) of a graph is the smallest minimum $st$-cut over all node pairs $st$. 
The size of the graph min-cut quantifies the connectivity of a graph,
but only incorporates information about edges lying on paths crossing the min-cut.
Instead, we use the mean size of all minimum $st$-cuts, which we refer to as the
{\em mean min-cut}.
This measure quantifies the number of redundant paths information can take through the network.
Networks with higher redundancy are more resilient to errors on one path \cite{albert_error_2000}
and allow innovations to propagate through complex contagion,
in which innovations are only adopted after multiple exposures through different sources
\cite{centola_complex_2007}.

The mean path and min-cutare computationally intensive,
requiring distance and minimum $st$-cut calculations for each all node pairs.
For larger projects, these calculations are impractical.
For large networks, we employed sampling to determine mean path length and mean
min-cut.
For mean path length, source nodes were sampled, and path length was calculated to all destination nodes
from each of these.
For min-cut, node pairs were sampled.
In both cases, stratification was used to ensure the same number of nodes were were sampled from each of
12 node degree quantiles.
We estimated the error due to sampling by determining true values for a medium-sized project,
and calculating error as a function of sample-size.
Sample sizes were chosen such that relative error was below 10\%.
Even with sampling, however, it was impractical to calculate these properties for the largest projects,
so we exclude the 183 largest projects from the analysis.
To control for bias in project size, we include several size-related variables in our models.

@@

To study the relationship between network structure, efficiency, and performance,
we model the performance and efficiency of WikiProjects using ordinary least-squares linear regression.
Each WikiProject is taken as a single observation.
The models include each project's coeditor network properties as independent variables.
We also include several project-level variables to control for confounding factors,
described below.
\begin{description}
\item[C-efficiency]
(Performance only.)
Quantifies how quickly a WikiProject improves articles.
Efficiencies for different grades are highly correlated,
so we include only one.
\item[Connected fraction]
Fraction of coeditor pairs connected by a path.
\item[Talk fraction] Fraction of total revisions made to talk pages.
\item[Mean similarity] Mean Jaccard similarity (by article) with other WikiProjects; a measure of topical complexity.
\item[Mean editors/article] Mean number of editors collaborating on each article in a WikiProject.
\item[Article count] Total number of articles in the WikiProject.
\item[Editor count] Total number of editors working on articles within a WikiProject.
\item[Revision count] Total number of revisions to articles in a WikiProject.
\item[First assessment] Timestamp of first assessment; a measure of how long a WikiProject has been active.
\item[Mean article age] Mean age of articles within a WikiProject.
\end{description}

Our models are summarized in Table \ref{tab:model}.
Min-cut is excluded from all models to avoid collinearity,
as it is highly correlated with degree.
In-degree and out-degree skewness were also highly correlated,
so we only include out-degree skewness in the models
(results are qualitatively similar).
Heavy-tailed variables are log-transformed.
To test the robustness of our results,
we also computed models using cube root instead of logarithmic transformations,
as well as using only top-importance and high-importance articles.
These robustness check yielded qualitatively similar results for all variables,
except for degree-skewness, which had an inconsistent sign across models.

@@

The negative dependence of performance on C-efficiency suggests there is generally a trade-off between
performance and efficiency.
However, low degree is correlated with both higher efficiency and higher performance,
suggesting that it is sometimes possible to improve both simultaneously.
Much of the existing numerical work on networked social learning focuses on path length rather than degree,
so we explore this result further using simulations in the next section.

@@

Without additional constraints,
the above model is missing
several key properties of real-world collaborations.
In designing our agent-based model, we paid attention to the
following properties, motivated by real-world collaborations.
\begin{description}
\item[Limited concern] Agents are concerned only with a subset of the entire
state when making decisions and determining preferences.
(On Wikipedia, editors typically interact with a small subset of the articles.)
\item[Concern-based network] Agents interact with other agents who share a
common concern over some subset of the state.
(On Wikipedia, editors interact with others who share interests in the same articles.)
\item[Unknown objective] Agents can rank states in order of preference,
but do not have access to the objective function.
(On Wikipedia, there is no ground truth measure of quality.)
\item[Single source of truth] At any given time, the system is in a single state
and agent preferences are based on local modifications to that state.
(At any point in time, there is only one current version of Wikipedia.)
\end{description}

@@

Learning strategies determine how agents update their preferences based on
available information.
Agents can engage in individual learning \cite{barkoczi_social_2016}
by applying a hill-climbing algorithm to their current solution.
In each iteration, one bit of the NK solution string is flipped to maximize the solution value.
If no change improves the value, the original solution is kept
The above strategy relies only on rankings of states,
satisfying the unknown objective assumption.
However, it does rely on information about the entire state,
violating the limited concern assumption.
In order to satisfy this assumption,
we also define a local variant
in which only a subset of bits in the NK solution string are considered.
This variant reflects a more realistic style of collaboration,
in which individual agents focus on sub-problems.

In social learning,
agents can also incorporate information from
other agents they are connected to by a network edge.
While individual learning always converges to the local maximum relative to the starting point,
social learning strategies allow agents to ``jump'' to drastically different solutions with higher local maxima.
In our model, we use both the conformity and best-neighbor strategies from \cite{barkoczi_social_2016}.
In the {\em best-neighbor} strategy, each agent compares its solution to a sample of its
neighbors, and chooses the solution with the highest value.
In order to compare solutions between neighbors,
the exact value of the objective function must be known for each solution,
so this strategy does not satisfy the unknown objective assumption
or the limited concern assumption.
In the {\em conformity} strategy, agents simply choose the most common solution among their neighbors
(ties are broken uniformly at random).
This strategy does not rely on solution value at all, so clearly satisfies the
unknown objective and limited concern assumptions.
In both cases, a single iteration of individual learning is performed after each social learning
iteration.
Because each agent maintains a separate estimate of the solution,
neither of these strategies satisfies the single source of truth assumption.

@@

In order to satisfy the single source of truth assumption,
we introduce a new strategy, which we call the local majority strategy.
In {\em local majority}, agents all begin with the same starting state,
and apply individual learning to their concern to generate
possible improvements to the solution.
Next, a new solution is constructed by considering each locus of the NK solution
individually.
Every agent concerned with a bit votes for its state based on their preferred
new solution and the majority state is chosen.
The result of this process is that all agents agree on a single improved state,
which forms the basis for the next iteration.
This strategy more realistically reflects collaborations like Wikipedia:
at any given time, a Wikipedia article has a single state, determined by consensus,
but editors may have differing opinions on how to improve that article.

@@

We simulated 100 trials for rewiring values of 0.0, 0.167, 0.333, 0.5, 0.667, 0.833, and 1.0.
For each trial we generated an NK model with N=250 and K=7 and ran each social learning strategy
(Table \ref{tab:strat}) for 300 iterations,
as well as a network based on that NK model and rewired.
For conformity and best-neighbor strategy, we used a sample size of 3, following
\cite{barkoczi_social_2016}.
We confirmed that all trials converged to their maximum value before reaching
the last iteration.
Networks had mean degree 116.6 with 1.3 standard deviation,
and mean path length of 1.766 with 0.0027 standard deviation.
The coefficient of variation of degree is approximately 10\%,
while only 1\% for mean path length, confirming that the rewiring process has a stronger influence
on degree than on path length.

@@

Figure \ref{fig:val-iter} shows how agents' solutions improve after repeated applications of
different learning strategies and rewiring values.
Each curve represents an average over 100 trials, each with 250 agent solutions.
The mean performance and efficiency are reported in Table \ref{tab:sim-eff-perf}.
For all rewiring values, local strategies are less efficient and more performant
than their non-local counterparts.
For the best-neighbor strategy, local outperforms global.
For local conformity strategy performs notably worse than all other strategies.
The local majority strategy is both more efficient and more performant than others,
with its performance increasing with higher rewiring.
These results imply that,
at least in a simple model of collaboration,
the performance and efficiency can be simultaneously increased.
Furthermore, performance and efficiency are potentially affected by both the choice of
learning strategy and the average degree of the agents' social network.

@@

While existing research into the role of network structure in collaboration
has focused on numerical simulations and lab experiments,
analysis of large real-world systems is an important next step.
Our empirical analysis of WikiProjects contributes several findings towards a better
understanding of large, decentralized, real-world collaboration.
We observe several results consistent with previous work:
a trade-off between performance and efficiency
\cite{mason_propagation_2008,grim_scientific_2013},
higher performance for shorter path lengths in a conformity setting
\cite{barkoczi_social_2016},
and a reduction in performance with increased structural inequality
\cite{kearns_experiments_2012}.
By using real-world networks, we were also able to analyze network properties independently,
allowing us to show that while most existing work has focused on the importance of path length,
degree distribution may be just as, or more, important.
The association of low-degree with both high performance and high efficiency is compelling,
as it sidesteps the usual trade-off between performance and efficiency.
In low-degree networks, agents have more repeated interactions with smaller groups of collaborators,
possibly suggesting that small team sizes could be beneficial for large collaborations.
Similarly, the observation that performance is higher in projects with less structural inequality suggests that,
if the challenges of egalitarian organizing can be overcome,
decentralized collaborations may produce better outcomes than those with centralized, top-down structures.

Our agent-based models offer a few additional insights.
We observe degree-dependent performance and efficiency dependence for both local conformity
and local majority strategies.
However, these two strategies have opposite degree dependence,
suggesting that different strategies may be preferable for high-degree and low-degree
networks.
Our local majority strategy,
designed to satisfy several properties present in real-world collaborations,
shows the strongest effects on performance and efficiency as network degree changes.
For the local majority strategy,
the relationship between degree and efficiency is consistent with our
empirical observations on Wikipedia,
suggesting one possible mechanism underlying that efficiency dependence.
However, the performance dependence of this strategy
is opposite that observed on Wikipedia,
suggesting that either the local majority strategy
is incompatible with actual behavior on Wikipedia or
that other factors (possibly including degree skewness)
outweigh the contribution of mean degree.

@@

A better understanding of the relationship between network structure and collaboration
outcomes has many practical applications.
Online communities using recommender systems to improve collaboration
could make recommendations guided by desirable network properties.
Similarly, network structure could be used to identify under-performing
groups in need of an intervention.
The relationship between network structure and learning strategy suggests that
behavioral norms interact with network structure.
This knowledge could be used by interventions to ensure that behavioral norms
and network structure are aligned for best performance and efficiency.

>>>>

The internet has enabled collaborations at a global scale.
Wikipedia, a free encyclopedia that invites anyone to edit articles,
is one of the most successful and visible examples of such a collaboration.
Organizing groups without top-down control is notoriously
difficult
\cite{freeman_tyranny_1972},
and yet Wikipedia, with millions of self-organized editors,
has produced a high-quality encyclopedia \cite{giles_internet_2005,keegan_evolution_2017}.
A better theoretical understanding of projects like Wikipedia is highly desirable as it could
help inform the design of new collaborative projects.
We focus on one aspect of a large-scale decentralized collaboration:
its network structure \cite{newman_structure_2003}.
How does Wikipedia's non-hierarchical structure relate to its success?

We look at WikiProjects on the English-language Wikipedia.
WikiProjects are collections of thematically related articles,
each with their own standards and norms.
When measuring the quality of collaborative projects,
there are at least two distinct measures to consider.
The first measure is short-term:
how effective a unit of work is at improving
the collaboration's output,
which we call {\em efficiency}.
The other measure is long-term:
the highest quality typically reached by an output,
which we call {\em performance}.
These two terms are often used interchangeably,
but we find it fruitful to distinguish between the two.
We find that Wikipedia exhibits an overall trade-off between performance and efficiency.
However, some WikiProjects are higher in both efficiency and performance
than others,
suggesting the existence of factors that correlate positively with both.

@@

Our main findings are:
\begin{itemize}
\item Despite an overall performance/efficiency trade-off,
WikiProjects having low-degree coeditor networks tend to have both higher performance and higher efficiency;
\item Short paths are associated with higher performance, consistent with a conformity-based learning strategy;
\item Structural inequality, as measured by degree skewness, is associated with lower performance;
\item Our agent-based model
shows that the efficiency and performance of collaborations can
depend on network degree,
and that the direction of that dependence varies with social learning strategy.
\end{itemize}

@@

\section{Background and Related Work}
\label{sec:background}
The present paper investigates the relationship between social networks
and collaboration outcomes.
This connection has been explored by a number of theoretical,
numerical, and small-scale lab studies in the field of
{\em social learning}.
We expand the literature with a large-scale, empirical field study.
In much of the existing literature,
degree distribution correlates with outcome measures.
But aside from the naive Bayes case, it is unknown whether
the correlation is explained best by degree or by another structural property, such as characteristic path length.
In the empirical networks we study,
unlike artificial networks,
the structural properties vary independently,
making it easier to isolate individual
network properties that correlate with outcome variables.

@@

{\bf Lab experiments.} Lab-based experiments on networked collaboration
suggest a complex interaction between network topology and other factors.
While groups of networked human subjects perform very well on
difficult graph-coloring tasks, the best performing network architectures
(e.g., fully-connected vs. small-world) vary
from task to task \cite{kearns_experiments_2012}.
The same studies found that while human subjects tend to perform well on
some networks, they perform worst on self-organized
networks.
Similarly, some network topologies are able to reach faster decisions in the
presence of more information, while others show the opposite effect
\cite{kearns_experimental_2006}.
Based on lab experiments, Fowler and Christakis \shortcite{fowler_cooperative_2010}
suggest that individual decisions towards altruism are conditional on their
neighbor's behavior and ``contagious'' up to three degrees away.
Later experiments by Suri and Watts \shortcite{suri_cooperation_2011} confirmed the
existence of conditional altruism,
but concluded that altruistic
behavior only influences first-degree neighbors.

@@

For Wikipedia specifically,
Robert and Romero \shortcite{robert_crowd_2015} found that
larger group sizes yield higher article ratings
when the groups are diverse and experienced. Kittur and Kraut found that different types of coordination have a complex
effect on the quality of Wikipedia articles \shortcite{kittur_harnessing_2008}.
Both explicit and implicit coordination result in higher quality articles,
with explicit coordination being especially central in the early life of an
article.
Shaw and Hill \shortcite{shaw_laboratories_2014}
found that behavior in online wiki communities is consistent
with the ``iron law of oligarchy,''
which states that
earlier members of a group will, over time, gain disproportionate
decision-making power and act increasingly out of self-interest rather than
the good of the group \cite{michels_political_1999}.
Similarly, Halfaker et al. \shortcite{halfaker_rise_2013} attributed decreasing
participation on Wikipedia to poor retention of new users.
Looking specifically at Wikipedia policies determined by editor consensus,
Keegan and Fiesler \shortcite{keegan_evolution_2017} found a trend
from flexible rule-making towards less flexible maintenance and deliberation.
Using content analysis,
Morgan et al. \shortcite{morgan_project_2013} found WikiProjects to be
more loosely organized than traditional teams.

@@

Our analysis combines multiple data
sets\footnote{Data and code at https://elplatt.com/a/WikiProject-Eff-Perf}
from the English-language Wikipedia.
For information about edit history, we used a publicly-available data set containing
metadata (time, article id, user) about all edits from July 12, 2006 to December 2, 2015.
We used a custom script to scrape article quality assessments from logs produced
by WP 1.0 Bot for 2279 unique WikiProjects
between May 4, 2006 and December 2, 2015.
Finally, we used a publicly-available database dump of page events (including rename events)
to reconstruct the article id for each title mentioned in the assessment logs.

@@

The {\em coeditor network} of a WikiProject consists of nodes representing editors,
and edges connecting any editors who have edited the same article.
The edges are directed, with the direction representing
{\em plausible information flow};
an edge from Alice to Bob exists if Alice edited an article and then Bob edited the same article at
a later time. Note that edges can exist in both directions. 
We make the simplifying assumption of unit weight for all edges.
We focus on three structural properties:
degree, characteristic path length, and min-cut.
Degree and characteristic path length have been shown to correlate with
performance and efficiency in some social learning settings
\cite{golub_naive_2010,mason_propagation_2008,grim_scientific_2013},
while min-cut can be interpreted as a measure of decentralization,
common feature of peer-produced communities such as Wikipedia
\cite{benkler_wealth_2006}.

The degree distribution is the simplest network property we analyze.
The in-degree (out-degree) of a node is the number of edges to (from) that node.
Taking the average of either in-degree or out-degree gives the same value:
the {\em mean degree} of the network.
In our context, the mean degree represents how many others a given editor has collaborated with.
We also consider the {\em skewness} of the in-degree and out-degree distributions.
A large positive degree skewness for a WikiProject coeditor network
implies that a small number of editors have a very large number of collaborators,
while a small positive value implies that the editors having the most collaborators
don't have many more than a typical editor.

We also calculate the characteristic path length for each WikiProject coeditor network.
The {\em distance} from node $s$ to node $t$ is the distance of the shortest path
from $s$ to $t$.
The {\em characteristic path length} (or just {\em path length})
is the mean distance between all editor pairs,
excluding unconnected pairs.
To account for unconnected nodes, we also measure the {\em connected fraction}:
the fraction of ordered node pairs with a directed path from source to sink.
The path length represents how quickly information can move through the network.
Networks with longer paths require more interactions for information to propagate,
which has been shown to reduce efficiency in some settings
\cite{mason_propagation_2008,barkoczi_social_2016}.

Our final network measure quantifies the connectivity of a project's coeditor network using
min-cut size.
The minimum $st$-cut between nodes $s$ and $t$ is the set of edges that must be removed in order that
no path exists from $s$ to $t$.
The minimum cut (min-cut) of a graph is the smallest minimum $st$-cut over all node pairs $st$. 
The size of the graph min-cut quantifies the connectivity of a graph,
but only incorporates information about edges lying on paths crossing the min-cut.
Instead, we use the mean size of all minimum $st$-cuts, which we refer to as the
{\em mean min-cut}.
This measure quantifies the number of redundant paths information can take through the network.
Networks with higher redundancy are more resilient to errors on one path \cite{albert_error_2000}
and allow innovations to propagate through complex contagion,
in which innovations are only adopted after multiple exposures \cite{centola_complex_2007}.

The mean path and min-cut are computationally intensive,
requiring distance and minimum $st$-cut calculations for each all node pairs.
For larger projects, these calculations are impractical and we thus employed sampling to determine mean path length and mean
min-cut.
For mean path length, source nodes were sampled, and path length was calculated to all destination nodes
from each of these.
For min-cut, node pairs were sampled.
In both cases, stratification was used to ensure the same number of nodes were were sampled from each of
12 node degree quantiles.
We estimated the error due to sampling by determining true values for a medium-sized project,
and calculating error as a function of sample-size.
Sample sizes were chosen such that relative error was below 10\%.
Even with sampling, however, it was impractical to calculate these properties for the largest projects,
so we exclude the 183 largest projects from the analysis.

@@

To study the relationship between network structure, efficiency, and performance,
we model the performance and efficiency of WikiProjects using ordinary least-squares linear regression.
Each WikiProject is a single observation.
The models include each project's coeditor network properties as independent variables.
We also include the following project-level variables to control for confounding factors.
\begin{description}
\item[C-efficiency]
(Performance only.)
Quantifies how quickly a WikiProject improves articles.
Efficiencies for different grades are highly correlated,
so we include only one.
\item[Connected fraction]
Fraction of coeditor pairs connected by a path.
\item[Talk fraction] Fraction of total revisions made to talk pages.
\item[Mean similarity] Mean Jaccard similarity (by article) with other WikiProjects; a measure of topical complexity.
\item[Mean editors/article] Mean number of editors collaborating on each article in a WikiProject.
\item[Article count] Total number of articles in the WikiProject.
\item[Editor count] Total number of editors working on articles within a WikiProject.
\item[Revision count] Total number of revisions to articles in a WikiProject.
\item[First assessment] Timestamp of first assessment; a measure of how long a WikiProject has been active.
\item[Mean article age] Mean age of articles within a WikiProject.
\end{description}

Our models are summarized in Table \ref{tab:model}.
Min-cut is excluded from all models to avoid collinearity,
as it is highly correlated with degree.
In-degree and out-degree skewness were also highly correlated,
so we only include out-degree skewness
(results are similar with in-degree skewness).
Heavy-tailed variables are log-transformed.
To test the robustness of our results,
we also computed models using cube root instead of logarithmic transformations,
and using only top- and high-importance articles.
The results were qualitatively similar results for all variables,
except for degree-skewness, which had an inconsistent sign across models.

@@

The negative dependence of performance on C-efficiency suggests there is generally a trade-off between
performance and efficiency.
However, low degree is correlated with both higher efficiency and higher performance,
suggesting that it is possible to improve both simultaneously.
Much of the existing numerical work on networked social learning focuses on path length rather than degree,
so we explore this result further using simulations in the next section.

@@

Without additional constraints,
the above model is missing
several key properties of real-world collaborations.
In designing our agent-based model, we paid attention to the
following properties.
\begin{description}
\item[Limited concern] Agents are concerned only with a subset of the entire
state when making decisions and determining preferences.
(On Wikipedia, editors typically interact with a small subset of the articles.)
\item[Concern-based network] Agents interact with other agents who share a
common concern over some subset of the state.
(On Wikipedia, editors interact with others who share interests in the same articles.)
\item[Unknown objective] Agents rank states in order of preference,
but do not have access to the objective function.
(On Wikipedia, there is no ground truth measure of quality.)
\item[Single source of truth] At any given time, the system is in a single state
and agent preferences are based on local modifications to that state.
(At any point in time, there is only one current version of Wikipedia.)
\end{description}

@@

Learning strategies determine how agents update their preferences based on
available information.
Agents can engage in individual learning \cite{barkoczi_social_2016}
by applying a hill-climbing algorithm to their current solution.
In each iteration, one bit of the NK solution string is flipped to maximize the solution value.
If no change improves the value, the original solution is kept.
The above strategy relies only on rankings of states,
satisfying the unknown objective assumption.
However, it relies on information about the entire state,
violating the limited concern assumption.
In order to satisfy this assumption,
we also define a local variant
in which only a subset of bits in the NK solution string are considered.
This variant reflects a more realistic style of collaboration,
in which individual agents focus on sub-problems.

In social learning,
agents can also incorporate information from
other agents they are connected to by an edge.
While individual learning always converges to the local maximum relative to the starting point,
social learning strategies allow agents to ``jump'' to drastically different solutions with higher local maxima.
In our model, we use both the conformity and best-neighbor strategies from \cite{barkoczi_social_2016}.
In the {\em best-neighbor} strategy, each agent compares its solution to a sample of neighbors, and chooses the solution with the highest value.
In order to compare solutions between neighbors,
the exact value of the objective function must be known for each solution,
so this strategy does not satisfy the unknown objective assumption
or the limited concern assumption.
In the {\em conformity} strategy, agents simply choose the most common solution among their neighbors
(ties are broken uniformly at random).
This strategy does not rely on solution value at all, so clearly satisfies the
unknown objective and limited concern assumptions.
In both cases, a single iteration of individual learning is performed after each social learning
iteration.
Because each agent maintains a separate estimate of the solution,
neither strategy satisfies the single source of truth assumption.

@@

To satisfy the single source of truth assumption,
we introduce a new strategy --- {\em local majority}.
In local majority, agents all begin with the same starting state and apply individual learning to their concern to generate
possible improvements to the solution.
Next, a new solution is constructed by considering each locus of the NK solution
individually.
Every agent concerned with a bit votes for its state based on their preferred
new solution and the majority state is chosen.
The result of this process is that all agents agree on a single improved state,
which forms the basis for the next iteration.
This strategy more realistically reflects collaborations like Wikipedia:
at any given time, a Wikipedia article has a single state, determined by consensus,
but editors may have differing opinions on how to improve that article.

@@

We simulated 100 trials for rewiring values of 0.0, 0.167, 0.333, 0.5, 0.667, 0.833, and 1.0.
For each trial we generated an NK model with $N=250$ and $K=7$ and ran each social learning strategy
(Table \ref{tab:strat}) for 300 iterations,
as well as a network based on that NK model and rewired.
For conformity and best-neighbor strategy, we used a sample size of 3, following
\cite{barkoczi_social_2016}.
We confirmed that all trials converged to their maximum value before reaching
the last iteration.
Networks had mean degree 116.6 with 1.3 standard deviation,
and mean path length of 1.766 with 0.0027 standard deviation.
The coefficient of variation of degree is approximately 10\%,
while only 1\% for mean path length, confirming that the rewiring process has a stronger influence
on degree than on path length.

@@

Figure \ref{fig:val-iter} shows how agents' solutions improve after repeated applications of
different learning strategies and rewiring values.
Each curve represents an average over 100 trials, each with 250 agent solutions.
The mean performance and efficiency are reported in Table \ref{tab:sim-eff-perf}.
For all rewiring values, local strategies are less efficient and more performant
than their non-local counterparts.
For the best-neighbor strategy, local outperforms global.
Local conformity performs notably worse than all others.
Local majority is both more efficient and more performant than others,
with its performance increasing with higher rewiring.
This implies that,
at least in a simple collaboration model,
the performance and efficiency can be simultaneously increased.
Furthermore, performance and efficiency are potentially affected by both the choice of
learning strategy and the average degree of the agents' social network.

@@

While existing research into the role of network structure in collaboration
has focused on numerical simulations and lab experiments,
analysis of large real-world systems is an important next step.
Our empirical analysis contributes several findings towards a better
understanding of large, decentralized, real-world collaboration.
We observe several results consistent with previous work:
a trade-off between performance and efficiency
\cite{mason_propagation_2008,grim_scientific_2013},
higher performance for shorter path lengths in a conformity setting
\cite{barkoczi_social_2016},
and a reduction in performance with increased structural inequality
\cite{kearns_experiments_2012}.
By using real-world networks, we were also able to analyze network properties independently,
allowing us to show that while most existing work has focused on the importance of path length,
degree distribution may be just as, or more, important.
The association of low-degree with both high performance and efficiency is compelling,
as it sidesteps the usual trade-off between performance and efficiency.
In low-degree networks, agents have more repeated interactions with smaller groups of collaborators, suggesting that small team sizes could be beneficial for large collaborations.
Similarly, the observation that performance is higher in projects with less structural inequality suggests that,
if the challenges of egalitarian organizing are overcome,
decentralized collaborations may produce better outcomes than those with centralized, top-down structures.

Our agent-based models offer a several insights.
We observe degree-dependent performance and efficiency dependence for both local conformity
and local majority strategies.
However, these two strategies have opposite degree dependence,
suggesting that different strategies may be preferable for high-degree and low-degree
networks.
Our local majority strategy,
designed to satisfy several properties in real-world collaborations,
shows the strongest effects on performance and efficiency as network degree changes.
For the local majority strategy,
the relationship between degree and efficiency is consistent with our
empirical observations on Wikipedia,
suggesting one possible mechanism underlying that efficiency dependence.
However, the performance dependence of this strategy
is opposite that observed on Wikipedia,
suggesting that either the local majority strategy
is incompatible with actual behavior on Wikipedia or
that other factors outweigh the contribution of mean degree.

@@

A better understanding of the relationship between network structure and collaboration
outcomes has practical applications.
Online communities using recommender systems could make recommendations guided by desirable network properties.
Similarly, network structure could be used to identify under-performing
groups in need of an intervention.
The relationship between network structure and learning strategy suggests that
behavioral norms interact with network structure, which could be used to ensure that behavioral norms
and network structure are appropriately aligned.
